All E\+AR package component behaviour is defined by a set of variables defined in the file /./conf/\+R\+E\+A\+D\+ME.md \char`\"{}ear.\+conf\char`\"{}. The components which allows parameters as an input will have priority against the configuration written in this file.

\subsection*{Environment variables list (deprecated) }

This is the old way to define the E\+AR behaviour. Its functionality is not guaranteed.

{\bfseries E\+AR}~\newline
 Enables or disables E\+AR by default.~\newline
 {\bfseries E\+A\+R\+\_\+\+D\+B\+\_\+\+P\+A\+T\+H\+N\+A\+ME}~\newline
 Defines the path to database saved files. These files stores all nodes metrics as data history, and its used to compute all nodes coefficients. They are not plain text files.~\newline
 {\bfseries E\+A\+R\+\_\+\+C\+O\+E\+F\+F\+\_\+\+D\+B\+\_\+\+P\+A\+T\+H\+N\+A\+ME}~\newline
 Defines the path to coefficients saved files. These files contains the coefficients of all nodes for all working frequencies.~\newline
 {\bfseries E\+A\+R\+\_\+\+U\+S\+E\+R\+\_\+\+D\+B\+\_\+\+P\+A\+T\+H\+N\+A\+ME}~\newline
 Defines the path to summary saved files. These files contains summaries of all executed applications as data historic. Can be read because they are plain text files.~\newline
 {\bfseries E\+A\+R\+\_\+\+D\+Y\+N\+A\+I\+S\+\_\+\+L\+E\+V\+E\+LS}~\newline
 Number of levels of Dyn\+A\+IS algorithm (see https\+://github.com/\+Barcelona\+Supercomputing\+Center/\+E\+A\+R/blob/development/src/library/\+R\+E\+A\+D\+M\+E.\+md \char`\"{}library page\char`\"{} for more information).~\newline
 {\bfseries E\+A\+R\+\_\+\+D\+Y\+N\+A\+I\+S\+\_\+\+W\+I\+N\+D\+O\+W\+\_\+\+S\+I\+ZE}~\newline
 Windows size of Dyn\+A\+IS algorithm (see https\+://github.com/\+Barcelona\+Supercomputing\+Center/\+E\+A\+R/blob/development/src/library/\+R\+E\+A\+D\+M\+E.\+md \char`\"{}library page\char`\"{} for more information).~\newline
 {\bfseries E\+A\+R\+\_\+\+L\+E\+A\+R\+N\+I\+N\+G\+\_\+\+P\+H\+A\+SE}~\newline
 Enables the learning phase.~\newline
 {\bfseries E\+A\+R\+\_\+\+M\+I\+N\+\_\+\+P\+E\+R\+F\+O\+R\+M\+A\+N\+C\+E\+\_\+\+E\+F\+F\+I\+C\+I\+E\+N\+C\+Y\+\_\+\+G\+A\+IN}~\newline
 Minimum performance efficiency gain for {\itshape M\+I\+N\+\_\+\+T\+I\+M\+E\+\_\+\+T\+O\+\_\+\+S\+O\+L\+U\+T\+I\+ON} policy in the form of percentage (e.\+g. 0.\+15 meaning 15\%). Could be overrided by {\ttfamily srun -\/-\/ear-\/policy-\/th} argument. It prevents switching the C\+PU to the next value in the range of available frequencies, if the performance increase indicator do not scale over this efficiency gain value, preventing the waste of energy.~\newline
 {\bfseries E\+A\+R\+\_\+\+P\+E\+R\+F\+O\+R\+M\+A\+N\+C\+E\+\_\+\+P\+E\+N\+A\+L\+TY}~\newline
 Maximum performance degradation for {\itshape M\+I\+N\+\_\+\+E\+N\+E\+R\+G\+Y\+\_\+\+T\+O\+\_\+\+S\+O\+L\+U\+T\+I\+ON} policy in the form of percentage (e.\+g. 0.\+15 meaning 15\%). Could be overrided by {\ttfamily srun -\/-\/ear-\/policy-\/th} argument. It means that prevents scalating the C\+PU to the next value in the range of available frequencies, if the performance degradation indicator of that frequency is over the penalty.~\newline
 {\bfseries E\+A\+R\+\_\+\+P\+O\+W\+E\+R\+\_\+\+P\+O\+L\+I\+CY}~\newline
 Sets by default an E\+AR policy. Could be overrided by {\ttfamily srun} arguments. The types are {\itshape M\+I\+N\+\_\+\+E\+N\+E\+R\+G\+Y\+\_\+\+T\+O\+\_\+\+S\+O\+L\+U\+T\+I\+ON}, which minimizes the energy consumed with a limit to the performance degradation ({\itshape E\+A\+R\+\_\+\+P\+E\+R\+F\+O\+R\+M\+A\+N\+C\+E\+\_\+\+P\+E\+N\+A\+L\+TY}), and {\itshape M\+I\+N\+\_\+\+T\+I\+M\+E\+\_\+\+T\+O\+\_\+\+S\+O\+L\+U\+T\+I\+ON}, which improves the execution time while guaranteeing a minimum performance efficiency that justifies more energy consumption ({\itshape E\+A\+R\+\_\+\+M\+I\+N\+\_\+\+P\+E\+R\+F\+O\+R\+M\+A\+N\+C\+E\+\_\+\+E\+F\+F\+I\+C\+I\+E\+N\+C\+Y\+\_\+\+G\+A\+IN}). The last policy is {\itshape M\+O\+N\+I\+T\+O\+R\+I\+N\+G\+\_\+\+O\+N\+LY}, just to analyze your application and get metrics.~\newline
 {\bfseries E\+A\+R\+\_\+\+P\+E\+R\+F\+O\+R\+M\+A\+N\+C\+E\+\_\+\+A\+C\+C\+U\+R\+A\+CY}~\newline
 Minimum time interval between two power measurements for a representative value.~\newline
 {\bfseries E\+A\+R\+\_\+\+R\+E\+S\+E\+T\+\_\+\+F\+R\+EQ}~\newline
 Set frequency to nominal at the begining of a new loop or not.~\newline
 {\bfseries E\+A\+R\+\_\+\+T\+U\+R\+BO}~\newline
 Enables turbo frequencies\+: those over the nominal frequency.~\newline
 {\bfseries E\+A\+R\+\_\+\+A\+P\+P\+\_\+\+N\+A\+ME}~\newline
 Default application name, used to save summarized metrics in DB.~\newline
 {\bfseries E\+A\+R\+\_\+\+T\+MP}~\newline
 Path were temporary files will be placed.~\newline
 {\bfseries E\+A\+R\+\_\+\+G\+U\+I\+\_\+\+P\+A\+TH}~\newline
 Path where the traces and graphic interface streaming files will be placed (see https\+://github.com/\+Barcelona\+Supercomputing\+Center/\+E\+A\+R/blob/development/src/library/\+R\+E\+A\+D\+M\+E.\+md \char`\"{}library page\char`\"{} for more information about the traces or G\+UI).~\newline
 {\bfseries E\+A\+R\+\_\+\+V\+E\+R\+B\+O\+SE}~\newline
 Defines the debug level. Higher the level, more messages.~\newline
 